\documentclass[12pt,letterpaper]{article}

% - default packages

% - \usepackage[backend=biber,style=apa]{biblatex}
\usepackage[doublespacing]{setspace}
\usepackage{indentfirst}
\usepackage{parskip}

% - \addbibresource{../bibliography.bib}

\title{\vspace*{-72pt}Final Writeup}
\author{Crystal Mandal}
\date{}

\begin{document}

\maketitle

This project is a reimagining of Stockhausen's \textit{Stimmung} 
for six cosine oscillators. Each voice is tuned justly to one of 
six notes sung in Stockhausen's \textit{Stimmung}. When the playback 
is initialised, each voice is started on an independent, random, 
``trigger". When a voice is triggered, it is given a new volume and 
a new ``vibrato" frequency (note: this is not true pitch vibrato, but 
is a parameter that slightly modulates volume above and below a given 
center to mimic the natural unsteadyness of a voice). Then, the voice's 
parameters slowly ramp from old parameters to the new ones. This ramp 
duration is set at 2 seconds. The duration between triggers is randomised 
from zero to five seconds. This gives the illusion of some stasis every 
couple of seconds, but constantly shifting voices. Note that the frequency 
of the pitches never changes; the only musical content comes from the 
shift in tone due to the manipulation of the volumes of particular 
overtones. Finally, a linear ramp envelope is added to automate a 
gradual fade to silence and to give the piece a duration. 

% - \nocite{*}

% - \printbibliography

\end{document}
